Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Move talk about specific geodata to Implementation
New evaluation and methodology section
Make research questions even clearer

This project has dealt with the feasibility of including footpath data when generating 3D representations of OSM data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.

The primary contribution is an \textbf{investigation into the rate of collision between map features in OSM}.
A program has taken an OSM dataset of the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.

For the collision study, see sections 1.3.1 for an implementation overview, 4.2 for a detailed walkthrough of the program implementation, and 5.1 for the results.

The secondary contribution will be an \textbf{assesment of the geometrical precision of OSM data} around the Stockholm area.
The positional accuracy will be estimated by comparing feature points between the OSM dataset and a reference dataset.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.

For the positional accuracy study, see sections 1.3.2 for an implementation overview, 4.1 for a walkthrough of the program implementation, and 5.2 for the results.

@@

@@

\chapter{The geodata used in this project}

\section{OSM data}

\section{SLU data}

\section{A word on coordinate systems}

\section{Specific geodata preprocessing}

\subsection{Quality criteria}

@@

>>>>

This project has dealt with the feasibility of including footpath data when generating 3D representations of OSM data, and preserving the integrity of the 3D road network, avoiding overlap and collision between road meshes.
The main contributions are as follows:

\begin{enumerate}
    \item The primary contribution is an \textbf{investigation into the rate of collision between map features in OSM}. How many roads of each type will collide with some other map feature once they have been given a geometrical width?
    \item The secondary contribution will be an \textbf{assesment of the geometrical precision of OSM data}. What is the positional accuracy of OSM map features compared to a reference map?
\end{enumerate}

For the primary contribution: the collision study, a program has taken an OSM dataset of the Stockholm area and assigned each road with standard withds according to swedish regulation.
It has then identified critical areas in the OSM dataset, where the paths are so wide that they collide with existing map features.
It has also identified how many of those areas can in theory be corrected by simple translation of the road vertices, without propagation of collision to other features.
Here, features are defined as the geometrical components that comprise the OSM map.
For the purpose of this report, features will refer mainly to roads and building footprints.
For the collision study, see sections 1.3.1 for an implementation overview, 4.2 for a detailed walkthrough of the program implementation, and 5.1 for the results.

For the secondary contribution: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM dataset and a reference dataset.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
For the positional accuracy study, see sections 1.3.2 for an implementation overview, 4.1 for a walkthrough of the program implementation, and 5.2 for the results.

@@

\chapter{Methodology and evaluation}

\section{Evaluation metrics}

@@

\section{Quality criteria}

@@

\section{The geodata used in this project}

\subsection{OSM data}

\subsection{SLU data}

\subsection{A word on coordinate systems}

\subsection{Specific geodata preprocessing}
